A non-contextual hidden variable model for Quantum Mechanics

### 2016-07-07 preReleases/version2/finalPaper.tex
removed redundancy, shifted more proofs to the appendix, added references, looked at the literature to ensure nothing was missed, fixed the BM section etc.

%% LyX 2.1.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[british,aps,superscriptaddress,nofootinbib,times,twocolumn]{revtex4-1}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=2cm,headsep=2cm,footskip=2cm}
\setcounter{secnumdepth}{3}
\usepackage{verbatim}
\usepackage{refstyle}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{esint}

@@

\title{A non-contextual hidden variable model for QM}

@@

\affiliation{Indian Institute of Science Education and Research (IISER), Mohali}
\begin{abstract}
We propose a non-contextual hidden variable model, consistent with all predictions of QM (for discrete spaces). We reconsider the no-go theorems on hidden variables and conclude that the notion of contextuality is not a necessary feature of quantum mechanics. Motivated by consistency requirements between Bohmian Mechanics and the said theorems, we provide an alternative view. This is accomplished by identifying a new classical property, we call `multiplicativity'. Advantages of this view are illustrated by considering the implications of non-multiplicativity to non-locality.%and its relation to contextuality.
\end{abstract}
\maketitle

>>>>

%% LyX 2.1.4 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[british,aps,prl,superscriptaddress,nofootinbib,times,reprint]{revtex4-1}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{geometry}
\geometry{verbose,tmargin=2cm,bmargin=2cm,lmargin=2cm,rmargin=2cm,headheight=2cm,headsep=2cm,footskip=2cm}
\setcounter{secnumdepth}{3}
\usepackage{verbatim}
\usepackage{refstyle}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{esint}

@@

\title{A non-contextual hidden variable model for Quantum Mechanics}

@@

\affiliation{Indian Institute of Science Education and Research (IISER), Mohali}
\begin{abstract}
We propose a non-contextual hidden variable model, consistent with all predictions of Quantum Mechanics (QM). We reconsider the no-go theorems on hidden variables and conclude that the notion of contextuality is not a necessary feature of quantum mechanics. Motivated by consistency requirements between Bohmian Mechanics and the said theorems, we provide an alternative view. This is accomplished by identifying a new classical property, we call `multiplicativity'. Advantages of this view are illustrated by considering the implications of non-multiplicativity to non-locality.%and its relation to contextuality.
\end{abstract}
\maketitle
